Ms 1

### 2017-09-01 ms1/ms1_display.Rmd
fixed or

est2pct = function(x) (exp(x) - 1)*100
mult_est = function(df, m) {
  mutate(df, estimate=m*estimate, std.error=sqrt(m)*estimate)
}
model_ci = function(df) {
  df %>%
    mutate(pct_change=est2pct(estimate),
           ci=1.96*std.error,
           ci_low=est2pct(estimate - ci),
           ci_high=est2pct(estimate + ci),
           change_str=sprintf('%.2f%% (%.2f -- %.2f%%)', pct_change, ci_low, ci_high))
}

@@

```{r pde_dx}
read_tsv('tables/dx_from_pde.tsv') %>% 
  spread(present, n) %>%
  mutate(pct=`TRUE`/(`TRUE` + `FALSE`)*100 %>% round(2)) %>%
  select(antibiotic, dx_cat, pct) %>%
  spread(dx_cat, pct) %>%
  head %>% kable
```

@@

```{r dx_to_pde_table}
dx_to_pde_unadj = read_tsv('tables/dx_rx_table.tsv') %>%
  filter(year %in% c(2011, 2014)) %>%
  select(dx_cat, antibiotic, year, f) %>%
  spread(year, f)

dx_to_pde_adj = read_tsv('tables/dx_rx_trends.tsv') %>%
  filter(term=='year') %>%
  mult_est(3) %>%
  mutate(ci=1.96*std.error,
         ci_low=estimate-ci,
         ci_high=estimate+ci) %>%
  select(dx_cat, antibiotic, estimate, ci_low, ci_high)

risk_ratio_f = function(or, p) or / (1 + p * (or - 1))

inner_join(dx_to_pde_unadj, dx_to_pde_adj, by=c('dx_cat', 'antibiotic')) %>%
  mutate(estimate=risk_ratio_f(estimate, `2011`),
         ci_low=risk_ratio_f(ci_low, `2011`),
         ci_high=risk_ratio_f(ci_high, `2011`),
         pct_change=(`2014`-`2011`)/`2011`) %>%
  mutate_if(is.numeric, function(x) round(x*100, 2)) %>%
  mutate(adj_change=sprintf('%.2f%% (%.2f -- %.2f%%)', estimate, ci_low, ci_high)) %>%
  select(dx_cat, antibiotic, `2011`, `2014`, pct_change, adj_change) %>%
  kable
```

Second, I do logistic regressions. The unit of analysis is the diagnosis. The outcome is whether a PDE for that drug follows a diagnosis in that category. The main predictor is year; covariates are as above. The adjusted percent change is between 2011 and 2014. (I computed this adjusted change, which is a relative risk, using the odds ratio from the regression and the mean probability of PDE for that diagnosis in 2011. This strictly incorrect: the mean relative risk is the mean of the risks computed using the predicted probabilities for each 2011 diagnosis, *not* the relative risk computed using the mean probability in 2011. But it seems like it's decently close, and I think insisting on the thing that is technically correct will only create confusion.)

I broke this into three tables by antibiotic, just to make it easier to navigate.

```{r dx_to_pde_trends}

```

>>>>

est2pct = function(x) (exp(x) - 1)*100
mult_est = function(df, m) {
  mutate(df, estimate=m*estimate, std.error=sqrt(m)*std.error)
}
model_ci = function(df) {
  df %>%
    mutate(pct_change=est2pct(estimate),
           ci=1.96*std.error,
           ci_low=est2pct(estimate - ci),
           ci_high=est2pct(estimate + ci),
           change_str=sprintf('%.2f%% (%.2f -- %.2f%%)', pct_change, ci_low, ci_high))
}

@@

```{r pde_dx}
read_tsv('tables/dx_from_pde.tsv') %>% 
  spread(present, n) %>%
  mutate(pct=`TRUE`/(`TRUE` + `FALSE`)*100 %>% round(2)) %>%
  select(antibiotic, dx_cat, pct) %>%
  spread(dx_cat, pct) %>%
  kable
```

@@

Second, I do logistic regressions. The unit of analysis is the diagnosis. The outcome is whether a PDE for that drug follows a diagnosis in that category. The main predictor is year; covariates are as above. The adjusted percent change is between 2011 and 2014. (I computed this adjusted change, which is a relative risk, using the odds ratio from the regression and the mean probability of PDE for that diagnosis in 2011. This strictly incorrect: the mean relative risk is the mean of the risks computed using the predicted probabilities for each 2011 diagnosis, *not* the relative risk computed using the mean probability in 2011.)

```{r dx_to_pde}
dx_to_pde_unadj = read_tsv('tables/dx_rx_table.tsv') %>%
  filter(year %in% c(2011, 2014)) %>%
  select(dx_cat, antibiotic, year, f) %>%
  spread(year, f)

dx_to_pde_adj = read_tsv('tables/dx_rx_trends.tsv') %>%
  filter(term=='year') %>%
  mult_est(3) %>%
  mutate(ci=1.96*std.error,
         ci_low=estimate-ci,
         ci_high=estimate+ci) %>%
  select(dx_cat, antibiotic, estimate, ci_low, ci_high) %>%
  arrange(dx_cat, antibiotic)

risk_ratio_f = function(odr, p) odr / (1 + p * (odr - 1))

inner_join(dx_to_pde_unadj, dx_to_pde_adj, by=c('dx_cat', 'antibiotic')) %>%
  # convert model estimates to odds ratios, then to risk ratios,
  # then to adjusted fractional changes, then to percentages
  mutate(or=exp(estimate),
         or_low=exp(ci_low),
         or_high=exp(ci_high),
         rr=risk_ratio_f(or, `2011`),
         rr_low=risk_ratio_f(or_low, `2011`),
         rr_high=risk_ratio_f(or_high, `2011`),
         adj_change=rr-1,
         adj_change_low=rr_low-1,
         adj_change_high=rr_high-1,
         pct_change=(`2014`-`2011`)/`2011`) %>%
  mutate_if(is.numeric, function(x) round(x*100, 2)) %>%
  mutate(adj_change=sprintf('%.2f%% (%.2f -- %.2f%%)', adj_change, adj_change_low, adj_change_high)) %>%
  select(dx_cat, antibiotic, `2011`, `2014`, pct_change, adj_change) %>%
  kable
```
